\bf Faster Neural Machine Translation Inference

### 2018-02-03 fast-beam/fast-beam.tex
fast beam paper

Fusing the softmax and beam search increase the speed of the output layer by 43\% for beam size 1, decreasing to 25\% for a beam of 10 when translating the Europarl dataset. This led to an overall increase in translation speed of up to 23\%, Figure~\ref{fig:beam-europarl}. Translation speed improved by up to 41\% when translating the Opensubtitles dataset, Figure~\ref{fig:beam-opensubtitles}. Compared to translating the Europarl test st, Figure~\ref{fig:pie-time-europarl} in Section~\ref{sec:Introduction}, the amount of time taken by the output layer dominates translation time for the OpenSubtitles test set, Figure~\ref{fig:pie-time-opensubtitles}.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{beam-opensubtitles.png}} 
\end{tabular}
\caption{Speed using the fused kernel (Opensubtitles)}
\label{fig:beam-opensubtitles}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-opensubtitles.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (Opensubtitles)}
\label{fig:pie-time-opensubtitles}
\end{figure}

>>>>

Fusing the softmax and beam search increase the speed of the output layer by 43\% for beam size 1, decreasing to 25\% for a beam of 10 when translating the Europarl dataset. This led to an overall increase in translation speed of up to 23\%, Figure~\ref{fig:beam-europarl}. Translation speed improved by up to 41\% when translating the OpenSubtitles dataset, Figure~\ref{fig:beam-opensubtitles}. Compared to translating the Europarl test st, Figure~\ref{fig:pie-time-europarl} in Section~\ref{sec:Introduction}, the amount of time taken by the output layer dominates translation time for the OpenSubtitles test set, Figure~\ref{fig:pie-time-opensubtitles}.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{beam-opensubtitles.png}} 
\end{tabular}
\caption{Speed using the fused kernel (OpenSubtitles)}
\label{fig:beam-opensubtitles}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-opensubtitles.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (OpenSubtitles)}
\label{fig:pie-time-opensubtitles}
\end{figure}
